---
title: "Dirofilaria Exploration"
author: "Jonathan Wilson"
date: "30/05/2020"
output: html_document
---

```{r}
library(readr)
library(here)
library(tidyverse)
library(GGally)
library(visdat)
library(magrittr)
library(gridExtra)
library(naniar)
library(ggmosaic)
library(ggplot2)
Diro<-read_csv("Dirofilaria_Dog_Data_5.29.20_update.csv")

Diro_col<-Diro[,-c(1,2,7,8,9,10,35,42)]


Diro_col[,c(3,5:28)] <- lapply(Diro_col[,c(3,5:28)], as.numeric)
```
```{r}
vis_miss(Diro_col)#i'm using viss miss to look for issing data

#ggpairs(Diro, columns = c(2,3,4,6,10:34))
#ggpairs isnt a good way to do this, we only want to know how each relates to DI status

# Diro$Dirofilaria[grep("os", Diro$Dirofilaria)] <- "TRUE" #chaged all positives to true
# Diro %<>%  mutate(Dirofilaria = recode(Dirofilaria, "Neg" = "FALSE", "0" = "FALSE"))
colnames(Diro_col)[1]<-"Dirofilaria"
Diro_col$Dirofilaria<-as.logical(Diro_col$Dirofilaria)
  

ggplot(Diro_col, aes(GPS_lat))+geom_histogram()

ggplot(Diro_col, aes(WBC))+geom_histogram()

 ggplot(Diro_col, aes(Dirofilaria , Agey))+geom_violin() + scale_y_continuous(limits = c(0, 20))

Diro_col$`Forest Cover`<-as.factor(Diro_col$`Forest Cover`) #recode forest cover as a facrotr 

Diro_col%<>% replace_with_na(replace = list(Sex = ".", Agey=c(99,0), BCS=c(0, 0.5),))  
#hi

 ggplot(Diro_col, aes(Dirofilaria , WBC))+geom_violin()# + scale_y_continuous(limits = c(0, 20))

  ggplot(Diro_col, aes(Dirofilaria , WBC))+geom_violin()# + scale_y_continuous(limits = c(0, 20))

Forest_infection<-ggplot(Diro_col)+geom_mosaic(aes(x=product(Dirofilaria, `Forest Cover`), fill=`Forest Cover`))+xlab("Forest Cover")+ylab("Dirofilaria Infection")

Forest_infection

ggsave(here::here("Forest_infection.png"),plot = Forest_infection)



ggplot(Diro_col,aes(Dirofilaria , WBC))+geom_boxplot()

ggplot(Diro_col,aes(Dirofilaria , HCT))+geom_boxplot() + scale_y_continuous(limits = c(0, 60))
class(Diro_col$Sex)
Diro_col$'Sex' <-as.factor(Diro_col$'Sex')

`
Dir
>  ggplot(data=Diro_col)+ 
+     + geom_mosaic(aes(x=product(Dirofilaria, 'Sex'),fill=Sex))+xlab("Sex")+ylab(Dirofilaria Infection)

R version 3.6.0 (2019-04-26) -- "Planting of a Tree"
Copyright (C) 2019 The R Foundation for Statistical Computing
Platform: x86_64-apple-darwin15.6.0 (64-bit)

R is free software and comes with ABSOLUTELY NO WARRANTY.
You are welcome to redistribute it under certain conditions.
Type 'license()' or 'licence()' for distribution details.

  Natural language support but running in an English locale

R is a collaborative project with many contributors.
Type 'contributors()' for more information and
'citation()' on how to cite R or R packages in publications.

Type 'demo()' for some demos, 'help()' for on-line help, or
'help.start()' for an HTML browser interface to help.
Type 'q()' to quit R.

[Workspace loaded from ~/Desktop/HW summer/Heartworm_2020/diro/.RData]

> library(ggplot2)
Warning message:
package ‘ggplot2’ was built under R version 3.6.2 
> library(ggmosaic)
> 
> ggplot(Diro_col,aes(Dirofilaria , Agey))+geom_violin() +
+ scale_y_continuous(limits = c(0,20))
Warning message:
Removed 24 rows containing non-finite values (stat_ydensity). 
> ggplot(Diro_col, aes(Dirofilaria , WBC))+geom_violin()# + scale_y_continuous(limits = c(0, 20))
Warning message:
Removed 29 rows containing non-finite values (stat_ydensity). 
> ggplot(Diro_col, aes(GPS_lat))+geom_histogram()
`stat_bin()` using `bins = 30`. Pick better value with `binwidth`.
Warning message:
Removed 11 rows containing non-finite values (stat_bin). 
> ggplot(Diro_col, aes(Dirofilaria , WBC))+geom_violin()# + scale_y_continuous(limits = c(0, 40))
Warning message:
Removed 29 rows containing non-finite values (stat_ydensity). 
> ggplot(Diro_col, aes(Dirofilaria , Sex))+geom_violin()
> ggplot(Diro_col, aes(Dirofilaria , Sex)) + geom_boxplot()
> ggplot(Diro_col, aes(Dirofilaria , Sex)) + geom_jitter()
> ggplot(Diro_col, aes(Dirofilaria , Sex)) + geom_bar()
Error: stat_count() can only have an x or y aesthetic.
Run `rlang::last_error()` to see where the error occurred.
> > ggplot(Diro_col, aes(Dirofilaria , Sex)) + geom_jitter()
Error: unexpected '>' in ">"
> ggplot(Diro_col, aes(Dirofilaria , Sex)) + geom_jitter()
> Forest_infection<-ggplot(Diro_col)+geom_mosaic(aes(x=product(Dirofilaria, `Sex`), fill=`Sex`))+xlab("Sex")+ylab("Dirofilaria Infection")
> Forest_infection<-ggplot(Diro_col)+geom_mosaic(aes(x=product(Dirofilaria, `Forest Cover`), fill=`Forest Cover`))+xlab("Forest Cover")+ylab("Dirofilaria Infection")
> Forest_infection<-ggplot(Diro_col)+geom_mosaic(aes(x=product(Dirofilaria, `Forest Cover`), fill=`Forest Cover`))+xlab("Forest Cover")+ylab("Dirofilaria Infection")
> Sex<-ggplot(Diro_col)+geom_mosaic(aes(x=product(Dirofilaria, `Sex`), fill=`Sex`))+xlab("Sex")+ylab("Dirofilaria Infection")
> Diro_col$`sex`<-as.factor(Diro_col$`Sex`) 
> 
> Diro_col$`Sex`<-as.factor(Diro_col$`Sex`)
> Diro_col$`Sex`<-as.factor(Diro_col$`Sex`)
> Diro_col$'Sex' <-as.factor(Diro_col$'Sex')
> class(Diro_col$Sex)
[1] "factor"
> Sex<-ggplot(Diro_col)+geom_mosaic(aes(x=product(Dirofilaria, `Sex`), fill=`Sex`))+xlab("Sex")+ylab("Dirofilaria Infection")
> 
> 
> Sex<-ggplot(Diro_col)+geom_mosaic(aes(x=product(Dirofilaria, `Sex`), fill=`Sex`))+xlab("Sex")+ylab("Dirofilaria Infection")
> Sex<-ggplot(Diro_col)+geom_mosaic(aes(x=product(Dirofilaria, 'Sex'), fill=Sex))+ xlab(Sex)+ylab("Dirofilaria Infection")
> ggplot(data=Diro) + 
+ geom_mosaic(aes(x= product(Sex), filled.contour(Sex))
+ 
+ s
Error: unexpected symbol in:
"
s"
> Sex<-ggplot(Diro_col)+geom_mosaic(aes(x=product(Dirofilaria, `Sex`), fill=`Sex`))+xlab("Sex")+ylab("Dirofilaria Infection")
> data(Dirofilaria)
Warning message:
In data(Dirofilaria) : data set ‘Dirofilaria’ not found
> data(diro)
Warning message:
In data(diro) : data set ‘diro’ not found
> data(Diro)
Warning message:
In data(Diro) : data set ‘Diro’ not found
> ggplot(data=Diro)+
+ geom_mosaic(aes(x=Diro_col, Sex))
Error: stat_mosaic() must not be used with a y aesthetic.
> ggplot(data=Diro_col)+ 
+ geom_mosaic(aes(x=product(Dirofilaria, 'Sex'),filled.contour(Sex)+xlab("Sex")+ylab(Dirofilaria Infection)
Error: unexpected symbol in:
"ggplot(data=Diro_col)+ 
geom_mosaic(aes(x=product(Dirofilaria, 'Sex'),filled.contour(Sex)+xlab("Sex")+ylab(Dirofilaria Infection"
> "ggplot(data=Diro_col)+ 
+ geom_mosaic(aes(x=product(Dirofilaria, 'Sex'),filled.contour(Sex)+xlab("Sex")+ylab(Dirofilaria Infection)
Error: unexpected symbol in:
""ggplot(data=Diro_col)+ 
geom_mosaic(aes(x=product(Dirofilaria, 'Sex'),filled.contour(Sex)+xlab("Sex"
>  ggplot(data=Diro_col)+ 
+     + geom_mosaic(aes(x=product(Dirofilaria, 'Sex'),filled.contour(Sex))+xlab("Sex")+ylab(Dirofilaria Infection)
Error: unexpected symbol in:
" ggplot(data=Diro_col)+ 
    + geom_mosaic(aes(x=product(Dirofilaria, 'Sex'),filled.contour(Sex))+xlab("Sex")+ylab(Dirofilaria Infection"
> ggplot(data=Diro_col)+ 
+     + geom_mosaic(aes(x=product(Dirofilaria, 'Sex'),filled.contour(Sex))+xlab("Sex")+ylab(Dirofilaria Infection)
Error: unexpected symbol in:
"ggplot(data=Diro_col)+ 
    + geom_mosaic(aes(x=product(Dirofilaria, 'Sex'),filled.contour(Sex))+xlab("Sex")+ylab(Dirofilaria Infection"
>  ggplot(data=Diro_col)+ 
+     + geom_mosaic(aes(x=product(Dirofilaria, 'Sex'),fill=Sex))+xlab("Sex")+ylab(Dirofilaria Infection)
Error: unexpected symbol in:
" ggplot(data=Diro_col)+ 
    + geom_mosaic(aes(x=product(Dirofilaria, 'Sex'),fill=Sex))+xlab("Sex")+ylab(Dirofilaria Infection"
> > ggplot(data=Diro_col)+ 
Error: unexpected '>' in ">"
>     +     + geom_mosaic(aes(x=product(Dirofilaria, 'Sex'),filled.contour(Sex))+xlab("Sex")+ylab(Dirofilaria Infection)
Error: unexpected symbol in "    +     + geom_mosaic(aes(x=product(Dirofilaria, 'Sex'),filled.contour(Sex))+xlab("Sex")+ylab(Dirofilaria Infection"
> 
> 
> Forest_infection<-ggplot(Diro_col)+geom_mosaic(aes(x=product(Dirofilaria, `Forest Cover`), fill=`Forest Cover`))+xlab("Forest Cover")+ylab("Dirofilaria Infection")
